Identify max rank for AUCell

### 2025-01-16 analyses/cell-type-ewings/exploratory_analysis/07-identify-max-rank-aucell.Rmd
remove seed and add comment about using percentage

# Set default ggplot theme
theme_set(
  theme_classic()
)

# set seed
set.seed(2025)
```

@@

- Prior to running `AUCell` we should remove any genes that are not detected in any cells.
- Using a cutoff of 1% of the total genes detected seems like a reasonable choice for the `aucMaxRank`.

>>>>

# Set default ggplot theme
theme_set(
  theme_classic()
)
```

@@

- Prior to running `AUCell` we should remove any genes that are not detected in any cells.
- Using a cutoff of 1% of the total genes detected seems like a reasonable choice for the `aucMaxRank`. 
This allows us to account for the variation in genes detected per sample, but we should be sure to be careful when interpreting results as using different cutoffs for each sample could impact the AUC values.
